High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
all run

add_models = Dict(
    "LeNet-5" => lenet,
    "RobustNet" => rob_net,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
    plot_factual = true,
    img_height = 150,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

>>>>

# CNN Ensemble:
lenet_ens = EnsembleModel(model=lenet, n=5)

add_models = Dict(
    "LeNet-5" => lenet,
    # "LeNet-5 Ensemble" => lenet_ens,
    # "RobustNet" => rob_net,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    # "LeNet-5 Ensemble",
    # "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
    plot_factual = true,
    img_height = 150,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
